Refunctionalization of Abstract Abstract Machines (Functional Pearl)

### 2018-07-04 paper/paper.tex
revision and update code

\subsubsection{Nondeterminism Abstraction}
We observe that in the refunctionalized AAM, @makeMCont@ actually repeats the prologue
part when matching a @let@ expression: they are both preparing a new environment and store 
for the body expression of a closure. %TODO motivation
We present a nondeterministic operator that abstracts this pattern:

>>>>

\subsubsection{Nondeterminism Abstraction}
We observe that in the refunctionalized AAM, @makeMCont@ is invoked with the tail part of
the closure set, and it actually repeats the code that creates the new environment and 
store for the body expression of a closure.
Based on observation, we present a nondeterministic operator that abstracts this pattern:
